---
title: "Homework 2"
subtitle: "Research in Health Economics, Spring 2024"
author: "Ria Dharnidharka"
format:
  pdf:
    output-file: "dharnidharka-r-hwk2-1"
    output-ext:  "pdf"
    header-includes:
      - \usepackage{float}
      - \floatplacement{table}{H}
---
```{r}
#| include: false

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, readr, readxl, hrbrthemes, fixest,
               scales, gganimate, gapminder, gifski, png, tufte, plotly, OECD,
               ggrepel, survey, foreign, devtools, pdftools, kableExtra, modelsummary,
               kableExtra)
```
```{r}
#| include: false
#| eval: true

 
load("Hwk2_workspace1.Rdata")
```
\newpage

\vspace{.2in}
\noindent 1. How many hospitals filed more than one report in the same year? Show your answer as a line graph of the number of hospitals over time.<br>

```{r}
#| echo: false
#| label: dup.hospitals
#| fig-cap: "Hospitals with Duplicates "

dup.hospitals
```
\newpage

\vspace{.2in}
\noindent 2. After removing/combining multiple reports, how many unique hospital IDs (Medicare provider numbers) exist in the data?

There are 48803 unique hospital ids in the dataset 

\newpage
\noindent 3. What is the distribution of total charges (tot_charges in the data) in each year? Show your results with a “violin” plot, with charges on the y-axis and years on the x-axis. For a nice tutorial on violin plots, look at Violin Plots with ggplot2.


```{r}
#| echo: false
#| label: totalcharges
#| fig-cap: "Distribution of Total Charges"

tot.charges
```
\newpage