---
title: "Homework 2"
subtitle: "Research in Health Economics, Spring 2024"
author: "Ria Dharnidharka"
format:
  pdf:
    output-file: "dharnidharka-r-hwk2-1"
    output-ext:  "pdf"
    header-includes:
      - \usepackage{float}
      - \floatplacement{table}{H}
---
```{r}
#| include: false

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, readr, readxl, hrbrthemes, fixest,
               scales, gganimate, gapminder, gifski, png, tufte, plotly, OECD,
               ggrepel, survey, foreign, devtools, pdftools, kableExtra, modelsummary,
               kableExtra)
```
```{r}
#| include: false
#| eval: true

 
load("Hwk2_workspace1.Rdata")
```
\newpage

\vspace{.2in}
\noindent 1. How many hospitals filed more than one report in the same year? Show your answer as a line graph of the number of hospitals over time.<br>

```{r}
#| echo: false
#| label: dup.hospitals
#| fig-cap: "Hospitals with Duplicates "

dup.hospitals
```
\newpage

\vspace{.2in}
\noindent 2. After removing/combining multiple reports, how many unique hospital IDs (Medicare provider numbers) exist in the data?

There are 48803 unique hospital ids in the dataset 

```{r}
#| include: false
#| eval: true

 
load("Hwk2_workspace1.Rdata")
```
\newpage

\newpage
\noindent 3. What is the distribution of total charges (tot_charges in the data) in each year? Show your results with a “violin” plot, with charges on the y-axis and years on the x-axis. For a nice tutorial on violin plots, look at Violin Plots with ggplot2.
```{r}
#| echo: false
#| label: tot.charges
#| fig-cap: "Total Charges"

tot.charges
```
\newpage

\newpage
\noindent 4. What is the distribution of estimated prices in each year? Again present your results with a violin plot, and recall our formula for estimating prices from class. Be sure to do something about outliers and/or negative prices in the data.
```{r}
#| echo: false
#| label: est.prices
#| fig-cap: "Estimated Prices"

est.prices
```
\newpage
